SummaryStats

### 2023-03-09 analysis/code/Exploration.Rmd
add minimal outcome exploration

```{r}
cities_life <- data %>% 
  group_by(city_id) %>% 
  summarise(
    years_exists = max(year) - min(year),
    rulers_count = n_distinct(terr_id),
    extinctions_count = sum(extinction),
    diffs_count = sum(count_diff != 0, na.rm=TRUE),
    mean_integ = mean(count_cities),
    lifetime_integ_diff = sum(count_diff, na.rm=TRUE),
    mean_yearly_diff = mean(count_diff, na.rm=TRUE),
    sd_yearly_diff = sd(count_diff, na.rm=TRUE)
    )

>>>>

cities_life <- data %>% 
  group_by(city_id) %>% 
  summarise(
    years_exists = max(year) - min(year),
    rulers_count = n_distinct(terr_id),
    extinctions_count = sum(extinction),
    diffs_count = sum(count_diff != 0, na.rm=TRUE),
    mean_integ = mean(count_cities),
    lifetime_integ_diff = sum(count_diff, na.rm=TRUE),
    mean_yearly_diff = mean(count_diff, na.rm=TRUE),
    sd_yearly_diff = sd(count_diff, na.rm=TRUE),
    lifetime_construction = sum(construction, na.rm=TRUE),
    across( # count non-missing observations of each outcome
      c(real_wage, welfare_ratio, construction), 
      ~ sum(!is.na(.x)),
      .names = "years_{.col}"
      )
    ) %>% 
  mutate(years_construction = years_construction * 25)
